A saturation model for impaired learning with enhanced plasticity: Supplementary material

### 2014-01-09 MHCpaper/MHCsupp.tex
VOR parameter fitting for serial model

    \cline{1-10}
    Serial   & 38 & $0.308$  & $0.21$  & $0.566$  & 0.488 & 0.775 & 0.211 & 1  & 4  &\label{tr:serial_fit} \\
    Cascade  & 14 & $0.386$  & $0.398$  & $0.466$  & 0.522 & 0.63 & 0.002 & 1.5  & 200  &\label{tr:cascade_fit} \\
    Non-uni. & 12 & $0.4$    & $0.4$    & $0.53$   & 0.5 & 0.7 & 0.1 & 5  & 500  &\label{tr:nonuni_fit} \\
    \cline{1-10}
  \end{tabularn}
 \end{center}
  \caption{Parameters used to reproduce detailed experimental results. For the sewrial model, the parameter listed is the transition probability between adjacent states. For the cascade and non-uniform multistate models, the parameter is the ratio of adjacent transition probabilities.} \label{tab:fit}
\end{table}

>>>>

    \cline{1-10}
    Serial   & 10 & $0.12$  & $0.14$  & $0.2$  & 0.5 & 0.11 & 0.89 & 5  & 100  &\label{tr:serial_fit} \\
    Cascade  & 14 & $0.386$  & $0.398$  & $0.466$  & 0.522 & 0.63 & 0.002 & 1.5  & 200  &\label{tr:cascade_fit} \\
    Non-uni. & 12 & $0.4$    & $0.4$    & $0.53$   & 0.5 & 0.7 & 0.1 & 5  & 500  &\label{tr:nonuni_fit} \\
    \cline{1-10}
  \end{tabularn}
 \end{center}
  \caption{Parameters used to reproduce detailed experimental results. For the sewrial model, the parameter listed is the transition probability between adjacent states. For the cascade and non-uniform multistate models, the parameter is the ratio of adjacent transition probabilities.} \label{tab:fit}
\end{table}
